\section{Sleep Stages}

\subsection{Number of Stages}
The human body cycles through two phases of sleep, (1) rapid eye movement (REM) and (2) non-rapid eye movement (NREM) sleep, which is further divided into three stages, N1-N3.\\[0.5cm]
N1, N2, N3, and REM. Stages N1 to N3 are considered non-rapid eye movement (NREM) sleep, with each stage a progressively deeper sleep. Approximately 75$\%$ of sleep is spent in the NREM stages, with the majority spent in the N2 stage. A typical night's sleep consists of 4 to 5 sleep cycles, with the progression of sleep stages in the following order: N1, N2, N3, N2, REM. A complete sleep cycle takes roughly 90 to 110 minutes. The first REM period is short, and, as the night progresses, longer periods of REM and decreased time in deep sleep (NREM) occur.\cite{4stage}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Stage} & \textbf{Percent} & \textbf{Amount of Time}\\ \hline
N1 (Light Sleep) & 5$\%$ & 1-5 minutes\\ \hline
N2 (Deeper Sleep) & 45$\%$ & 25 minutes \\ \hline
N3 (Deepest Sleep) & 25$\%$ & 30-60 minutes \\ \hline
REM & 25$\%$ & $\geq$10 minutes \\ \hline
\end{tabular}
\caption{Time Period for Each Stage}
\label{tab:my_label_with_H_tag}
\end{table}

\subsection{Activities in Each Stage}
\begin{itemize}
    \item \textbf{Stage 1:} Light sleep. This is a short stage, usually no more than 5$\%$ of your total sleep, which begins right after you fall asleep.
    \item \textbf{Stage 2:} Deeper sleep. This stage is deeper and makes up about 45$\%$ of all the time you spend sleeping (this number goes up as you get older). Research indicates this stage is key in memory storage and learning.
    \item \textbf{Stage 3:} Deepest sleep. This stage makes up about 25$\%$ of the time you spend sleeping. This stage is the most important to how your body recovers and maintains itself because the brain prioritizes this stage in people with sleep deprivation. It’s very hard to wake someone up from this stage, and they’ll usually feel foggy or confused for up to 30 minutes after waking up.
    \item \textbf{REM sleep:} REM stands for “rapid eye movement.” This stage is when you dream. When a person is in REM sleep, you can see their eyes moving beneath their eyelids.
\end{itemize}

\subsection{Sequence of Sleep Stages}
\begin{enumerate}
    \item Sleep begins with NREM stage 1 sleep.
    \item NREM stage 1 progresses into NREM stage 2.
    \item NREM stage 2 is followed by NREM stage 3.
    \item NREM stage 2 is then repeated.
    \item Finally, you are in REM sleep.\cite{sequence}
\end{enumerate}